Pass 3 Comparison

### 2025-04-09 index.qmd
rendered the html versions

The study report is available [manuscript/manuscript.qmd](manuscript/manuscript.qmd) document.

@@

Commonly used datasets [manuscript/datasets.qmd](manuscript/datasets.qmd).

>>>>

The study report is available at [manuscript/manuscript.qmd](manuscript/manuscript.qmd) document.

@@

Commonly used datasets are available at [manuscript/datasets.qmd](manuscript/datasets.qmd).

### 2025-04-09 studies/search_syntax.qmd
rendered the html versions

Out of the studies identified in the first pass, a closer look at the priority 2 studies using the criteria established [link to prereg] was carried out.

>>>>

Out of the studies identified in the first pass, a closer look at the priority 2 studies using the criteria established in the [preregistration plan](preregistration/preregistration.qmd) was carried out.
